---
title: "tidbitr"
author: "Prabhuram Venkatesan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

`tidbitr` offers handy functions that will be a shorthand for data analysis.

- Clipboard functions `CopyFromClipboard` and `CopyToClipboard` to read and write to clipboard
- `Freq` returns a frequency table based on all the columns in a dataset
- `Recon` reconciles and compares between two dataset for differences in them. Similarly operator`%=%` merges and compares two datasets
- `Stat` returns statistical summary of all the columns in a dataset. Stats includes # of rows, mean, median, N/A values, etc.
- `GetXMLNodes` gets text of all XML nodes
- `NumWithComma` class that can coerce numbers with comma as numbers when reading from files

## CopyToClipboard

```{r}
library(dplyr)
library(tidbitr)

census %>%
  tidbitr::CopyToClipboard(quote = F) 
```

Similarly `CopyFromClipboard` can be used to read dataframe contents from the clipboard.

## Freq

```{r}
Freq(census)
Freq(census)$State
Freq(census, 50, "d") 
```


## Recon

```{r}
list1
list2
Recon(list1, list2)
```

## Stat

```{r}
Stat(mtcars)
```

## GetXMLNodes

```{r}
GetXMLNodes(xml2::read_xml("https://www.w3schools.com/xml/simple.xml"))
GetXMLNodes(xml2::read_xml("https://www.w3schools.com/xml/simple.xml"), "calories")
```

Check the [xml](https://www.w3schools.com/xml/simple.xml) yourself
